---
title: "Quality Control of different mascot outputs"
output: html_document
---

##Setup
```{r}
library(plyr)
library(tidyverse)
source("R/00 - sources_utility.R")
```

*All R functions, scripts and data used can be found under*
*https://github.com/kbajdzienko/Phosphoproteomics*

*All mascot CSV files are stored in DATA/DATA_F011845.zip*


#Mascot OUTPUT 1

> FILE: F011845.csv

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | ACTIVE |
|Sameset protein families  | OFF    |
|Ions score cut-off        | OFF    |
|Group protein families    | ACTIVE |
|Show duplicate peptides        | ACTIVE |
|Require Bold Red          | OFF    |

*This is default Mascot OUTPUT we use (setup by server administrator)*

```{r}
QC_stat_mascot("DATA/F011845.csv")

plot_QC_hist_mascot("DATA/F011845.csv")
```

#Mascot OUTPUT 2

> FILE: F011845_ions10.csv*

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | ACTIVE |
|Sameset protein families  | OFF    |
|Ions score cut-off        | **10** |
|Group protein families    | ACTIVE |
|Show duplicate peptides    | ACTIVE |
|Require Bold Red          | OFF    |

```{r}
QC_stat_mascot("DATA/F011845_ions10.csv")

plot_QC_hist_mascot("DATA/F011845_ions10.csv")
```

#Mascot OUTPUT 3

> FILE: F011845_br.csv*

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | ACTIVE |
|Sameset protein families  | OFF    |
|Ions score cut-off        | OFF    |
|Group protein families    | OFF    |
|Show duplicate peptides        | ACTIVE |
|Require Bold Red          | ACTIVE |

```{r}
QC_stat_mascot("DATA/F011845_br.csv")

plot_QC_hist_mascot("DATA/F011845_br.csv")
```

#Mascot OUTPUT 4

> FILE: F011845_br_ions10_ndp_nspf.csv*

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | OFF |
|Sameset protein families  | OFF    |
|Ions score cut-off        | **10**  |
|Group protein families    | OFF   |
|Show duplicate peptides        | OFF |
|Require Bold Red          | ACTIVE |

```{r}
QC_stat_mascot("DATA/F011845_br_ions10_ndp_nspf.csv")

plot_QC_hist_mascot("DATA/F011845_br_ions10_ndp_nspf.csv")
```
