---
title: "Uncertainties in mascot queries"
output: word_document
---

##Setup
```{r}
library(tidyverse)
source("R/01.2 - read_mascot.R")

query_dupes <- function(mascot_tbl = mascot){
  message("Total number of queries:", distinct(mascot_tbl, query_number)%>%nrow())
  message("Table with duplicate queries:")
  mascot_tbl %>%
  group_by(query_number) %>%
  filter(n() > 1) %>%
  arrange(query_number, desc(pep_score)) %>%
  return()
}
query_choice <- function(mascot_tbl = mascot, query_tbl = query){
  message("Total number of queries:", distinct(query_tbl, query_number)%>%nrow())
  message("Table with problematic queries:")
  query_tbl %>%
  semi_join(mascot_tbl, "query_number") %>%
  group_by(query_number) %>%
  filter(n() >= 2) %>%
  filter(sum(!is.na(pep_score)) >= 1) %>%
  filter(pep_score == max(pep_score, na.rm = T)) %>%
  ungroup() %>%
  anti_join(mascot_tbl, c("query_number", "pep_score")) %>%
  arrange(desc(pep_score)) %>%
  return()
}
```

*All R functions, scripts and data used can be found under*
*https://github.com/kbajdzienko/Phosphoproteomics*


*All mascot CSV files are stored in DATA/DATA_F011845.zip*



#Mascot OUTPUT 1

> FILE: F011845.csv

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | ACTIVE |
|Sameset protein families  | OFF    |
|Ions score cut-off        | OFF    |
|Group protein families    | ACTIVE |
|Show duplicate peptides        | ACTIVE |
|Require Bold Red          | OFF    |


*This is default Mascot OUTPUT we use (setup by server administrator)*

##Case 1: More than one peptide from the same query(MS/MS scan) in final output
```{r}
mascot <- read.mascot("DATA/F011845.csv", "pep")
query_dupes()
```


##Case 2: Query result with lower score is picked for mascot peptide table
```{r}
query <- read.mascot("DATA/F011845.csv", "query")
query_choice()
```
### Confirmation on an example: 923
```{r}
filter(mascot, query_number == "923") %>% select(query_number, pep_score, everything())
filter(query, query_number == "923") %>% select(query_number, pep_score, pep_var_mod_conf, everything())
```

Here a peptide with peptide score of 8.4 and no pep_var_mod_conf is picked from the queries. A peptide with score 32.23 and 86.88 confidence is being skiped and cannot be found in mascot report.

```{r}
filter(mascot, pep_seq == "ASSFIR")
```


#Mascot OUTPUT 2

> FILE: F011845_ions10.csv*

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | ACTIVE |
|Sameset protein families  | OFF    |
|Ions score cut-off        | **10** |
|Group protein families    | ACTIVE |
|Show duplicate peptides    | ACTIVE |
|Require Bold Red          | OFF    |

##Case 1: More than one peptide from the same query (MS/MS scan) in final output
```{r}
mascot <- read.mascot("DATA/F011845_ions10.csv")
query_dupes()
```

##Case 2: Query result with lower score is picked for mascot peptide table
```{r}
query <- read.mascot("DATA/F011845_ions10.csv", "query")
query_choice()
```

### Confirmation on an example: 31335
```{r}
filter(mascot, query_number == "31335") %>% select(query_number, pep_score, everything())
filter(query, query_number == "31335") %>% select(query_number, pep_score, pep_var_mod_conf, everything())
```


#Mascot OUTPUT 3

> FILE: F011845_br.csv*

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | ACTIVE |
|Sameset protein families  | OFF    |
|Ions score cut-off        | OFF    |
|Group protein families    | OFF    |
|Show duplicate peptides        | ACTIVE |
|Require Bold Red          | ACTIVE |

##Case 1: More than one peptide from the same query (MS/MS scan) in final output
```{r}
mascot <- read.mascot("DATA/F011845_br.csv")
query_dupes()
```

##Case 2: Query result with lower score is picked for mascot peptide table
```{r}
query <- read.mascot("DATA/F011845_br.csv", "query")
query_choice()
```
### Confirmation on an example: 5306
```{r}
filter(mascot, query_number == "5306") %>% select(query_number, pep_score, everything())
filter(query, query_number == "5306") %>% select(query_number, pep_score, pep_var_mod_conf, everything())
```

#Mascot OUTPUT 4

> FILE: F011845_br_ions10_ndp_nspf.csv*

| Setting                  | Status  |
|--------------------------|:------:|
|Subset protein families   | OFF |
|Sameset protein families  | OFF    |
|Ions score cut-off        | **10**  |
|Group protein families    | OFF   |
|Show duplicate peptides        | OFF |
|Require Bold Red          | ACTIVE |

##Case 1: More than one peptide from the same query (MS/MS scan) in final output
```{r}
mascot <- read.mascot("DATA/F011845_br_ions10_ndp_nspf.csv")
query_dupes()
```

##Case 2: Query result with lower score is picked for mascot peptide table
```{r}
query <- read.mascot("DATA/F011845_br_ions10_ndp_nspf.csv", "query")
query_choice()
```
### Confirmation on an example: 23770
```{r}
filter(mascot, query_number == "23770") %>% select(query_number, pep_score, everything())
filter(query, query_number == "23770") %>% select(query_number, pep_score, pep_var_mod_conf, everything())
```

